%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Flynt Wallace} \\ \vspace{1pt}
    \small 678-673-9656 $|$ \href{flyntwallace77@gmail.com}{\underline{flyntwallace77@gmail.com}} $|$ 
    \href{linkedin.com/in/flyntdubu}{\underline{linkedin.com/in/flyntdubu}} $|$
    \href{github.com/flyntdubu}{\underline{github.com/flyntdubu}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Georgia Institute of Technology}{Atlanta, GA}
      {Masters of Science in Computer Science, Computing Systems}{Aug. 2023 -- May 2024 (est.)}
    \resumeSubheading
      {Georgia Institute of Technology}{Atlanta, GA}
      {Bachelors of Science in Computer Science, Systems-Architecture/Media, GPA: 3.71}{Aug. 2019 -- May 2023}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}

\resumeSubHeadingListStart

\resumeSubheading
  {Graduate Teaching Assistant}{August 2023 -- Present}
  {Georgia Institute of Technology}{Atlanta, GA}
  \resumeItemListStart
            \resumeItem{Assisting students in the understanding of mobile and ubiquitous computing, including \textbf{machine learning}, \textbf{Arduino} development, and \textbf{XR} related technologies.}
            \resumeItem{Mentoring 6 student teams, facilitating innovative \textbf{embedded systems} \& \textbf{machine learning} projects.}
  \resumeItemListEnd

    \resumeSubheading
      {XR Master}{August 2022 -- Present}
      {Flowers Invention Studio}{Atlanta, GA}
      \resumeItemListStart
                \resumeItem{Supervising the largest student run makerspace in the country, training students and faculty across 14 distinct tool groups facilitating personal, research, and academic projects.}
        \resumeItem{Spearheading the foundation of the first dedicated XR space in Georgia Tech, managing a \$100k budget.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Web Development Intern}{Jun. 2023 -- Aug. 2023}
      {Ideas United}{Atlanta, GA}
      \resumeItemListStart
        \resumeItem{Contributed to the development of a SaaS platform utilized by over 2000 users, with multiple Fortune 500 partners such as Google, PlayStation, Starbucks, and Warner Bros. Discovery.}
        \resumeItem{Utilized \textbf{Ruby on Rails}, \textbf{PostgreSQL}, and \textbf{Vue.js} to add new functionality using the Google Drive API, perform secure database modifications, identify and implement bugfixes, and create 15+ custom components.}
    \resumeItemListEnd

    \resumeSubheading
      {Web Accessibility Consultant}{May 2021 -- Dec. 2021}
      {Mesmer Eyes, Inc.}{Remote}
      \resumeItemListStart
              \resumeItem{Conducted thorough WCAG compliance audits for mobile apps, including five Fortune 500 clients.}
        \resumeItem{Developed \textbf{Java} software for automated AI detection of mobile app accessibility violations.}
        \resumeItem{Created \textbf{Android} and \textbf{iOS} applications to explore and test WCAG failure \& success scenarios.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
    \resumeProjectHeading
          {\textbf{KitBit} $|$ \emph{Arduino, Rust, Python, TensorFlow}}{January 2023 -- Present}
          \resumeItemListStart
                      \resumeItem{Co-founded a wearable activity tracker for indoor cats using an LSTM model to to track pet health and detect irregularities in a minimally-invasive manner.}
                        \resumeItem{Extending the  project to create a modular framework for researchers to conduct studies with robust sensor data \& ML implementations through the Georgia Tech ACI Lab.}
            \resumeItem{Authored a 14-page research paper to be presented and published in the 2023 ACI Conference.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{TAI} $|$ \emph{Python, OpenAI, Fly.io}}{October 2023}
          \resumeItemListStart
                      \resumeItem{Leveraged the Canvas API and \textbf{GPT-4} to develop a personalized Teaching Assistant AI using retrieval-augmented generation to cite course documents in answer generation, deployed using \textbf{Fly.io}.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{TransferApp} $|$ \emph{TypeScript, React, Next.js, Firebase}}{August 2021 -- May 2022}
          \resumeItemListStart
            \resumeItem{Designed and developed a web app for Emory to improve the transfer process of patients between medical institutions in a HIPAA-compliant manner using end-to-end encryption.}
            \resumeItem{Awarded 1st place among all Fall ’22 junior design projects at Georgia Institute of Technology.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Tron: Disc Wars} $|$ \emph{Unity, Photon, Oculus SDK}}{March 2023}
          \resumeItemListStart
            \resumeItem{Created a co-location multiplayer mixed reality Oculus Quest game developed for the ImmerseGT hackathon.}
                        \resumeItem{Awarded 1st place in the Virtual Adventures track, in a competition with 550+ applicants.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, C/C++, C\#, Python, NASM (x86, x86-64), TypeScript, Ruby, HTML/CSS, Rust, SQL} \\
     \textbf{Frameworks}{: React, Node.js, Flask, D3.js, Vue, Rails, Processing, Next.js, Pandas, TensorFlow} \\
     \textbf{Tools}{: Git, Docker, Unity, Arduino, PostgreSQL, Heroku, Fly.io, NumPy, Jupyter, Ghidra, IDA, AWS, Android Studio} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
